\name: Deterministic and Coherent Implicits

### 2017-02-09 Main.tex
Proofs
fix latex problem
acmlarge style
make bibliography work
various small fixes
local
macro for name
change title
remove comment
ACM classification

\documentclass[sigplan, anonymous, review]{acmart}
%\documentclass[prodmode,acmtoplas]{acmsmall}

\usepackage{color}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{stmaryrd}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{mathpartir}
\usepackage{wasysym}
\usepackage{url}
\usepackage{algorithm, algpseudocode}
\usepackage{fancyvrb}
%\usepackage[[style=1]{mdframed}
\usepackage{comment}
\usepackage{soul}

@@

% Title portion
\title{The Implicit Calculus: A New Foundation for Generic Programming}
\author{Ommitted for anonymous submission}

\begin{abstract}
\input{src/Abstract}
\end{abstract}

@@

\input{src/SourceLang}

%\input{src/Related}

@@

% Bibliography
\bibliographystyle{ACM-Reference-Format}
\bibliography{sigproc}

%\input{src/Proofs}

>>>>

\documentclass[acmlarge, anonymous, review]{acmart}
%\documentclass[prodmode,acmtoplas]{acmsmall}

\usepackage{color}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{stmaryrd}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{mathpartir}
\usepackage{wasysym}
\usepackage{url}
\usepackage{algorithm, algpseudocode}
\usepackage{fancyvrb}
%\usepackage[[style=1]{mdframed}
\usepackage{comment}
\usepackage{soul}

@@

% Title portion
\title{\name: Deterministic and Coherent Implicits}
\author{Ommitted for anonymous submission}

\begin{abstract}
\input{src/Abstract}
\end{abstract}
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10010124.10010125.10010130</concept_id>
<concept_desc>Theory of computation~Type structures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011008.10011009.10011012</concept_id>
<concept_desc>Software and its engineering~Functional languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Type structures}
\ccsdesc[500]{Software and its engineering~Functional languages}

@@

%\input{src/SourceLang}

\input{src/Related}

@@

% Bibliography
\bibliographystyle{ACM-Reference-Format}
\bibliography{papers}

\input{src/Proofs}
